Approximation as Differentiation notes

### 2025-02-21 notes/definitions.tex
CMon isn't Cartesian closed but there is a commutative monoid structure on the hom-objects.

A \emph{commutative monoid} $A = (A, \varepsilon, +)$ is a set equipped with distinguished element
$\varepsilon \in A$ called the \emph{unit} and associative binary operation $+$ satisfying $\varepsilon + x =
x$ and $x + \varepsilon = x$ for any $x \in A$.

@@

Although $\CMon$ is not Cartesian closed, every hom-object $\CMon(A,B)$ is a commutative monoid, with the
constant homomorphism that sends every element of the carrier of $A$ to $1_A$ as the unit, and pointwise
multiplication as the binary operation.

>>>>

A \emph{commutative monoid} $A = (A, \varepsilon, +)$ is a set equipped with distinguished element
$\varepsilon \in A$ called the \emph{unit} and associative binary operation $+$ satisfying $\varepsilon + x =
x$ and $x + \varepsilon = x$ for any $x \in A$. A commutative monoid homomorphism from $A$ to $B$ is any
function $f: A \to B$ which preserves $\varepsilon$ and $+$.

@@

Although $\CMon$ is not Cartesian closed, every hom-object $\CMon(A,B)$ is a commutative monoid, with unit
given by the constant homomorphism that sends every element of $A$ to $\varepsilon_B$, and binary operation
given by $(f + g)(a) = f(a) + f(b)$.
